PCA on Finnish Municipalities

### 2022-04-10 MSA-Project.Rmd
Optimized figure quality

```{r screeplot, echo=FALSE, fig.cap="Variance explained by each Princial Component (PC) up to the 20th PC. This type of a plot is also known as a Scree Plot", optipng = '-o7'}

@@

Figure \@ref(fig:loadingsplot2) shows the loading directions for PCs 3 and 4.
```{r scoreplot1, echo=FALSE, message=FALSE, fig.cap="Score plot for all municipalities that have a top 5 absolute loading in any of PC1 and PC2", fig.align='center'}

@@

```{r loadingsplot1, warning=FALSE, echo=FALSE, fig.cap="Loading directions for PC1 and PC2", fig.align='center'}

@@

```{r scoreplot2, echo=FALSE, message=FALSE, fig.cap="Score plot for all municipalities that have a top 5 absolute loading in any of PC3 and PC4", fig.align='center'}

@@

```{r loadingsplot2, warning=FALSE, echo=FALSE, fig.cap="Loading directions for PC3 and PC4", fig.align='center'}

>>>>

```{r screeplot, echo=FALSE, fig.cap="Variance explained by each Princial Component (PC) up to the 20th PC. This type of a plot is also known as a Scree Plot", fig.align='left', optipng = '-o7'}

@@

Figure \@ref(fig:loadingsplot2) shows the loading directions for PCs 3 and 4.
```{r scoreplot1, echo=FALSE, message=FALSE, fig.cap="Score plot for all municipalities that have a top 5 absolute loading in any of PC1 and PC2", fig.align='left', optipng = '-o7'}

@@

```{r loadingsplot1, warning=FALSE, echo=FALSE, fig.cap="Loading directions for PC1 and PC2", fig.align='left', optipng = '-o7'}

@@

```{r scoreplot2, echo=FALSE, message=FALSE, fig.cap="Score plot for all municipalities that have a top 5 absolute loading in any of PC3 and PC4", fig.align='left', optipng = '-o7'}

@@

```{r loadingsplot2, warning=FALSE, echo=FALSE, fig.cap="Loading directions for PC3 and PC4", fig.align='left', optipng = '-o7'}
